cardinalR: Generating interesting high-dimensional data structures

### 2025-08-23 paper-cardinalR.Rmd
Added data for some of data structures

```{r, eval=FALSE}
langevitour::langevitour(cone)
```

@@

```{r, label = "fig-cone-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `cone` data."}
#| fig-width: 15
#| fig-height: 5

@@

```{r, eval=FALSE}
langevitour::langevitour(gau)
```

@@

```{r, label = "fig-gau-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `gau` data."}
#| fig-width: 15
#| fig-height: 5

@@

```{r, eval=FALSE}
langevitour::langevitour(linear)
```

@@

```{r, label = "fig-linear-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `linear` data."}
#| fig-width: 15
#| fig-height: 5

@@

```{r mobius-proj, fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `mobius` data."}
#| fig-width: 15
#| fig-height: 5

>>>>

```{r}
cone_lang <- langevitour::langevitour(cone, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r cone, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `cone` data in $4\\text{-}D$."}

conefig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    cone_lang
  ),
  device = "xs"
)

class(conefig) <- c(class(conefig), "htmlwidget")

conefig
```

```{r cone-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `cone` data."}
#| fig-width: 15
#| fig-height: 5

@@

```{r}
gau_lang <- langevitour::langevitour(gau, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r gau, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `gau` data in $4\\text{-}D$."}

gaufig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    gau_lang
  ),
  device = "xs"
)

class(gaufig) <- c(class(gaufig), "htmlwidget")

gaufig
```

```{r gau-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `gau` data."}
#| fig-width: 15
#| fig-height: 5

@@

```{r}
linear_lang <- langevitour::langevitour(linear, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r linear, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `linear` data in $4\\text{-}D$."}

linearfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    linear_lang
  ),
  device = "xs"
)

class(linearfig) <- c(class(linearfig), "htmlwidget")

linearfig
```

```{r linear-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `linear` data."}
#| fig-width: 15
#| fig-height: 5

@@

```{r mobius-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `mobius` data."}
#| fig-width: 15
#| fig-height: 5

### 2025-08-23 paper-cardinalR.tex
Added data for some of data structures

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-cone-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `cone` data.}\label{fig:fig-cone-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-gau-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `gau` data.}\label{fig:fig-gau-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-linear-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `linear` data.}\label{fig:fig-linear-proj}
\end{figure}

>>>>

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/cone-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `cone` data.}\label{fig:cone-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/gau-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `gau` data.}\label{fig:gau-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/linear-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `linear` data.}\label{fig:linear-proj}
\end{figure}
